How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-12 tse-paper/abstract.tex

Build logs are textual by-products that a software build process
creates, often as part of its Continuous Integration (CI)
pipeline. Build logs are a paramount source of information for
developers when debugging into and understanding a build
failure. Recently, attempts to partly automate this time-consuming,
purely manual activity have come up, such as rule- or
information-retrieval-based techniques.

We evaluate and compare three different techniques that aim to retrieve
specified log parts (chunks) from a build log, namely program synthesis
by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on the manually
labeled \emph{LogChunks} data set.
Our findings show that none of the three techniques in general outperforms
the others. We discuss under which circumstances each technique performs best
and provide a recommendation on when developers or researchers should use which
technique.

>>>>

Build logs are the textual by-product that a software build process
creates, often as part of its Continuous Integration (CI)
pipeline. Build logs can not only serve as a paramount source of
information for developers to understand and debugging into build or
test failures, but also for automated on-ward processing. Manually
extracting the important chunks of information, though, is akin to
finding a needle in a haystack. Recently, attempts to partly automate
this time-consuming activity have come up, such as rule- or
information-retrieval-based techniques.
In this paper, we first sysmetically overview and categorize the existing methods to extract information chunks. We then develop prototypical implementations for three promising techniques, namely program synthesis
by example, textual similarity and search keywords. We evaluate them in an empirical study on the manually
labeled \emph{LogChunks} data set, which comprises more than x build logs in y languages.
Our findings show that none of the three techniques in general outperforms
the others. We discuss under which circumstances each technique performs best
and provide a recommendation on when developers or researchers should use which
technique.
